Co-citations in context

### 2019-06-13 cocit_r.tex
Minor revisions

Of relevance, we found the category displaying the highest hit rate to be sensitive to the study parameters, which are the percentage of articles classified as hits and the z-score percentile threshold that delineates LN and HN. \textcolor{blue}{(data not shown).} Faced with this lack of robustness, we are confronted with the necessity of defining defendable parameters, if possible, that determine novelty and conventionality.  More significantly, we should question whether the simple approach of defining novelty and conventionality, as is done in this article and other research, is sufficient or whether we should expect such variation in the factors associated with impact as we have observed.

>>>>

Of relevance, we found the category displaying the highest hit rate to be sensitive to the study parameters, which are the percentage of articles classified as hits and the z-score percentile threshold that delineates LN and HN. \textcolor{blue}{(data not shown).} This lack of robustness makes parameter selection of the utmost importance.  However, the most appropriate definitions of novelty, conventionality, and hit articles in the framework that we have applied are not clear.  More research might be done in that regard or, further, in investigating whether the current approach of defining novelty, conventionality, and impactful research sufficiently captures the complexity of the issue at hand.
